### 2019-05-25 Literature_Review/pages/review_content.tex
Changes; - Added more content to the literature review

The authors decision to exclude hexadecimal and numerical encodings (some of the most widespread encoding schemes) was due to their similarity to Base32 and their well known deficiencies. This is not consistent with available research where, for example in \textit{``Empirical Study of Textual Key-Fingerprint Representations''}) it was shown numerical representations performed better than that of Base32.

Overall, findings from the paper showed that age and gender does not affect the accuracy of the scheme, however younger participants were significantly faster. \\
The paper recommends Base32, Random Art, T-Flag or their own improvement; Flag Ext. These encoding recommendations were also supplemented with a review of requirements required by these schemes. The recommendation of graphical encoding schemes is inconsistent with alternative literature, where most other papers have found graphical encodings hard to use and insecure.
In terms of language comprehension; being able to speak the language assists in the ability to discern the different between hard pairs. Knowledge of the language subsequently did not help with easy pairs.

In conclusion, the paper provided a very strong foundation for further research due to the wide variety of topics touched upon. However, its age means that results cannot be applicable to modern day scenarios, and oversights in the development of the study such as the exclusion of hexadecimal encoding and the lack of information gained on the perceived usability of the scheme from users results in an incomplete study of these encoding schemes.

@@

Overall, if usability is the only consideration the paper ranked the comparison methods like so: Compare-and-Confirm, Compare-and-Enter, Compare-and-Select and Barcode. If, however, the consideration of security alongside usability is required the best is Compare-and-enter, Barcode, Compare-and-Confirm and Compare-and-Select. Research has been limited in this area of modes of comparison, however, the results from this paper are consistent with the alternative literature.
\\
In terms of encoding schemes the paper ranked Numerical, Alphanumerical and Words as the top three encoding schemes (These were all with Compare-and-Confirm). This took into consideration the usability and security of the scheme. This is relatively consistent with other literature where numerical and written encoding schemes seem to be the most effective overall.

@@

With changes to the UX of Confirm-and-Confirm backed up by external research \cite{palmer1990attentional}\cite{hammer2009category} the second round of research was performed with a new set of participants.

Overall, the changes took Confirm-and-Confirm from 20\% to 0\% fatal error rate (FER). The same trend for Confirm-and-Select with it reducing its FER from 12.5\% to 5\%. With the changes the participants perceived the systems as easy to use. The authors therefore recommended Confirm-and-Confirm as the overall best choice for comparison methods. Again, comparing this word to the most similar work done by Kainda \textit{et al.}\cite{kainda2009usability} this is consistent with their findings where they ranked Compare-and-Confirm as more secure compared to that of Compare-and-Select.

Overall, the paper provides a sizeable insight into suitable methods of comparison, this is due to the cross over fingerprint comparison and secure device pairing have. This paper is limited in terms of the short strings compared, the different overall research aim and the size of the number of participants used in the studies. In terms of security of the schemes the results were constant with that of alternative research but clashed when usability was considered. This, however, may be due to the differing use-cases of the comparison methods and the sizes of strings being compared.

@@

Other references made within the paper touch upon the vulnerabilities and usability issues present with the way humans interact with the security systems. Example of these are studies showing humans find it difficult to comprehend long and "meaningless" strings and the lack of actual comparison performed by actual users in live scenario's. These are, however, acknowledged as limitations in the later stages of the paper.

@@

Overall, results from the experiments emulated previously discussed literature. Textual representations faired effectively well with Words and Sentences again being some of the best options overall. Performance of graphical representation was mixed with OpenSSH having performance matching that of a strong textual mapping while Unicorns having the worst performance overall. This performance with graphical representations is consistent with the available literature apart from the positive performance of OpenSSH. The results of different modes of comparison was highly consistent with other studies where again the recommendation was to not use compare-and-select as its performance across the board was below even simple levels of security.

>>>>

The authors decision to exclude hexadecimal and numerical encodings (some of the most widespread encoding schemes) was due to their similarity to Base32 and their well known deficiencies. This is not consistent with available research. For example, in \textit{``Empirical Study of Textual Key-Fingerprint Representations''} it was shown numerical representations performed better than that of Base32.

Overall, findings from the paper showed that age and gender does not affect the accuracy of the scheme, however younger participants were significantly faster. \\
The paper recommends Base32, Random Art, T-Flag or their own improvement; Flag Ext. These encoding recommendations were also supplemented with a review of requirements required by these schemes. The recommendation of graphical encoding schemes is inconsistent with alternative literature, where most other papers have found graphical encodings easy to use but insecure.
In terms of language comprehension; being able to speak the language assists in the ability to discern the differences between hard pairs. Knowledge of the language subsequently did not help with easy pairs.

In conclusion, the paper provided a very strong foundation for further research due to the wide variety of topics touched upon. However, its age means that results cannot be applicable to modern day scenarios, and oversights in the development of the study such as the exclusion of hexadecimal encoding and the lack of information gained on the perceived usability of the scheme from users results in an ultimately incomplete study.

@@

Overall, if usability is the only consideration the paper ranked the comparison methods like so: Compare-and-Confirm, Compare-and-Enter, Compare-and-Select and Barcode. If, however, the consideration of security alongside usability is required the best is Compare-and-Enter, Barcode, Compare-and-Confirm and Compare-and-Select. Research has been limited in this area of modes of comparison, however, the results from this paper are consistent with the alternative literature.
\\
In terms of encoding schemes the paper ranked Numerical, Alphanumerical and Words as the top three encoding schemes (These were all with Compare-and-Confirm). This took into consideration the usability and security of the scheme. This is relatively consistent with other literature where numerical and written encoding schemes seem to be the most effective overall.

@@

With changes to the UX of Confirm-and-Confirm backed up by external research \cite{palmer1990attentional}\cite{hammer2009category} the second round of research was performed with a new set of participants. The alterations took Compare-and-Confirm from 20\% to 0\% fatal error rate (FER). The same trend for Confirm-and-Select with it reducing its FER from 12.5\% to 5\%. With the changes the participants perceived the systems as easy to use. The authors therefore recommended Compare-and-Confirm as the overall best choice for comparison methods. Again, comparing this word to the most similar work done by Kainda \textit{et al.}\cite{kainda2009usability} this is consistent with their findings where they ranked Compare-and-Confirm as the most secure comparison method.

Overall, the paper provides a sizeable insight into suitable methods of comparison, this is due to the cross over between fingerprint comparison and secure device pairing. This paper is limited in terms of the short strings compared, the different overall research aim and the size of the number of participants used in the studies. In terms of security of the schemes the results were constant with that of alternative research but clashed when usability was considered. This, however, may be due to the differing use-cases of the comparison methods and the sizes of strings being compared.

@@

Other references made within the paper touch upon the vulnerabilities and usability issues present with the way humans interact with the security systems. Example of these are studies showing humans find it difficult to comprehend long and "meaningless" strings and the lack of actual comparison performed by users in live scenarios. These are, however, acknowledged as limitations in the later stages of the paper.

@@

Overall, results from the experiments emulated previously discussed literature. Textual representations faired effectively well with Words and Sentences again being some of the best options overall. Performance of graphical representation was mixed with OpenSSH having performance matching that of a strong textual mapping while Unicorns having the worst performance overall. This performance with graphical representations is consistent with the available literature apart from the positive performance of OpenSSH. The results of different modes of comparison was highly consistent with other studies where again the recommendation was to not use Compare-and-Select as its performance across the board was below even basic levels of security.

\textbf{TODO: } Summarise research section

\section{Fingerprint encoding schemes}
Another area of research is investigation into the actual physical encodings of the hash digest. This section will briefly discuss the current research available on the creation and security of actual encoding schemes. The actual details of operation of the schemes are outside the scope of this literature review, therefore, minimal attention will be allocated to these details.

Some of the oldest preliminary work into visual encoding schemes was performed by Adrian Perrig \textit{et al}\cite{perrig1999hash}. in the creation of their scheme ``Random Art" in 1999. The motivation for creating such a scheme was the perceived flaws in the ways humans verify information and compare written information. As mentioned in previous sections visual encoding schemes have been shown to have mixed success, with low security being one of their most alarming flaws. This research laid the foundation for further work in analysing the security of visual encoding schemes (as discussed in the previous section) to the creation of new schemes.

Further research into creation of unique visual hash schemes have been performed by C Ellison \textit{et al.} \cite{ellison2003public} (Flag), Yue-Hsun Lin \textit{et al.}\cite{lin2010spate} (T-Flag) and work by MM Olembo \textit{et al.}\cite{olembo2013developing}. Each publication has provided a new way to visually represent a key fingerprint. This list is by no means exhaustive but is used to depict amount of research into this topic.

One paper of note is the preliminary work performed by D Loss \textit{et al.}\cite{loss2009drunken} in their \textit{``An analysis of the OpenSSH fingerprint visualization algorithm''} where their aim was to spur on further research with their initial findings into the security of the OpenSSH scheme. The authors claim that the use of the algorithm in OpenSSH is only heuristically defined and there is a need for a formal proof of its security.

The paper proposed a number of ways to generate similar fingerprints. The methods proposed were: Naive brute force, graph theory methods, and brute force of a full visual set. They were able to produce only very basic results and have proposed a large amount of potential further work. Since the papers publication in 2009, there seems to have been no publications building on the work of the authors. This highlights a current gap in the available literature.

Minimal research has also focused on textual fingerprint representations and their respective security. Work by A. Karole and N. Saxena\cite{karole2009improving} is the only relevant research looking into ways to improve the security of a textual representation. This research aim is to improve the secure device pairing process of comparing two numerical values. The devices used (Nokia 6030b - Mid range devices at the time of publication) and short SAS compared results in findings that only slightly applicable in a fingerprint comparison context.

Aside from this research there has been no other publications exploring the security textual representations. This clearly shows the presence of a sizeable research gap in the available literature.

{\small \textbf{TODO: } \textit{Need to double check this, I think there might have been some work into sentences}}

In conclusion to this topic, the current research has primarily focused on the research and creation of visual representations. This leaves a previously mentioned research gap for anything focusing primarily on the security and usability of encoding schemes such as words, or sentences.

### 2019-05-25 Papers/Notes_TeX/pages/paper_notes.tex
Changes; - Added more content to the literature review

>>>>

\newpage

\section{The drunken bishop: An analysis of the OpenSSH
fingerprint visualization algorithm}

The aim of this research is to study the OpenSSH Visual Host Key. The authors claim that the scheme was heuristically designed and has very little backing in terms of formal research, this paper aims to create a foundation for this research.

OpenSSH uses MD5 to generate a 128-bit fingerprint of the Server's key, this is then split into 64 2-bit pairs. These are then traversed byte wise in a right to left over the bit pairs. Each pair defines the direction of travel. If the snake reaches a position multiple times a pre define character is added depending on the number of visits (for example, 6 times == "B")

The paper also discusses ways to create collisions:

In conclusive results and more of an inital PoC

\begin{itemize}
    \item Brute force
    \item Graph theory
    \item Brute forcing a visual set
\end{itemize}

\newpage

\section{Improving the Robustness of Wireless Device
Pairing Using Hyphen-Delimited Numeric
Comparison}

In the context of secure device pairing the paper aims to improve the human interaction with number pairing.

Lots of research has gone into Short Authentication String (SAS) numbers ([14], [10], [4])

The research was peformed on very old devices. Nokia 6030b, very out of date and not reflective of anything around at this time.

Usability study looked into Efficiency, Robustness, General Usability

Strange format of keeping the numbers exactly the same but just placing hyphens in the middle. The authors attempted to remedy this by spacing the experiments with a days gap

Study was performed with 40 participants

Very small number of values tested only 5 overall???

Initial results show promising results for hypen delimitations etc alongside improved user impressions
